---
title: "Question 1"
author: "Ramzan Kamoto"
date: "2024-06-18"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1 

For the first part of this question I try to establish the most popular names nationally per decade. I start by creating a function that creates a tibble, which gives me the name with the highest count in every decade. I then use that table to construct a simple bar chart with names in the x axis and years on the y axis. 



```{r}
#load relevant data and packages 
library(tidyverse)

list.files('/Users/ramzankamoto/Documents/Masters/DS_EXAM/23550716/Question1/code', full.names = T, recursive = T) %>% as.list() %>% walk(~source(.))

custom_names <- c("Baby_Names", "charts", "population_data","HBO_credits","HBO_titles")

read_rds_files("/Users/ramzankamoto/Documents/Masters/DS_EXAM/23550716/Question1/data", custom_names)
```

## Plot

```{r}
#use highest count function to find the name with the highest count per decade
highest_count_table <- highest_count_per_decade(data_frame = Baby_Names)
```

Admittedly, this is likely an over simplification. It might have been better to take the aggregate of all named Mary for example, rather than simply taking the highest figure. 


```{r}
Names_per_decade_plot <- plot_highest_names(highest_count_table)

print(Names_per_decade_plot)

##This plot still needs to be improved. Check Nicos slides on tidy visualizations.
```
## Spearmans correlation

For the next part, we calculate the Spearmans rank correlation. It measures the magnitude and direction of of association between two variabales. 


```{r}

#creating a dataframes for top 25 names in 1995 and 1998
top_names <- create_top_names_datasets(Baby_Names)
top_25_males_1995 <- top_names$males_1995
top_25_females_1995 <- top_names$females_1995
top_25_males_1998 <- top_names$males_1998
top_25_females_1998 <- top_names$females_1998
```

Next we conduct the spearman correlation 

```{r}
cor.test(top_25_males_1995$Count, top_25_males_1998$Count, method = "spearman")

cor.test(top_25_males_1998$Count, top_25_females_1998$Count, method = "spearman")

```
The spearman correlation is suggesting, perfect positive correlation for any combination of top names in 1995 and 1998. There is likely an error in my calculation. 








