---
title: "Question 3"
author: "Ramzan Kamoto"
date: "2024-06-18"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 3 loading in data 

First load and view the appropriate datasets.  

```{r}
alloc <- read_csv("/Users/ramzankamoto/Documents/Masters/DS_EXAM/23550716/Question3/data/Ukraine_Aid/Financial Allocations.csv")
commit <- read_csv("/Users/ramzankamoto/Documents/Masters/DS_EXAM/23550716/Question3/data/Ukraine_Aid/Financial Commitments.csv")

```

For this question I will compare EU countries with Rest of the World (RoW) by creating a plot bubble plot that shows which countries have allocated more resources as a percentage of GDP. 

First create a new dataframe with our variables of interest.

```{r}
new_commit <- commit %>% 
    select(Country,`EU member` ,`GDP in 2021($ billion)`,`Total bilateral commitments($ billion)`) %>% 
    mutate(commit_per_gdp = `Total bilateral commitments($ billion)`/`GDP in 2021($ billion)`*100)
```

 
We then clean up the data a little so that it is less error prone. 

```{r}
commit_df <- new_commit %>% 
    rename(country = Country,
           eu_member =`EU member`,
           gdp = `GDP in 2021($ billion)`,
           commit_gdp = commit_per_gdp
           )
```

Use bubble plot function on our new dataframe 

```{r}
plot_gdp_vs_commit(commit_df)
```
From the plot we can clearly see that most EU nations are committing less than 1 % of their GDP to aid Ukraine. Only five countries commit more than 1 % of their total GDP and these countries all have relatively small GDP's. 

From this we might suggest that EU nations could be doing more to aid Ukraine in this war. 

Next we run a simple regression to see how strong the effect that being an EU member has on total bilateral allocation controlling for all other variables. 



First we clean up the data again.  

```{r}
# Slightly messy but renames variables to be more usable.
alloc_df <- alloc %>% 
    rename(country = Country,
           eu_member = `EU member`,
           fin_alloc = `Financial allocations($ billion)`,
           humanitarian_alloc = `Humanitarian allocations($ billion)`,
           military_alloc = `Military allocations($ billion)`,
           total_bi_alloc = `Total bilateral allocations($ billion)`,
           share_eu_alloc = `Share in EU allocations($ billion)`) %>% 
    select(-country)

```

Our linear regression 

```{r}
ols_model1 <- lm_eu_effect(alloc_df, "total_bi_alloc", control_vars = c("fin_alloc","humanitarian_alloc","military_alloc"))

print(ols_model1)

```
Now we wish to make the table neater and more presentable, so we make use of the broom and kable packages. 

```{r}
# library(broom)
# library(kableExtra)
# 
# tidy_model <- broom::tidy(ols_model1)
#   print(tidy_model)
#   
# clean_model <- tidy_table(tidy_model) 
# 
# print(clean_model)

# Come back to this, doesnt really look that lakker
```






